Incremental λ-Calculus in Cache-Transfer Style

### 2017-07-11 popl18/source-language.tex
Grammar

In Figure~\ref{fig:source-definition-base-terms-semantics}, the base
terms are evaluated using a step-indexed big-step semantics whose
judgment~$\seval\sectx\sterm{n}\sclosedvalue$ is read ``Under the
environment~$\sectx$, the base term~$\sterm$ evaluates into the closed
value~$\sclosedvalue$ in~$n$~steps.''
%
\rulename{SVar} looks up into~$\sectx$ to return the closed value of a
variable~$\tx$.
%
\rulename{STuple} looks up for~$\many\tx$ into~$\sectx$ to evaluate
the tuple~$\stuple{\many\tx}$, binds it to~$\ty$ and continues with
the next term.
%
\rulename{SPrimitiveCall} assumes that~$\tf$ is mapped to a
primitive~$\sprim$ in~$\sectx$ and that $\sprim$ has an associated
interpretation realized as a function~$\tdelta\sprim\param$ from
closed values to closed values. The evaluation of this interpretation
function applied to the value of~$\tx$ is bound to~$\ty$ in~$\sectx$
in order to evaluate the remaining term~$\sterm$ in~$n$ steps. In that
case, the evaluation of the $\textbf{let}$-binding takes~$n + 1$~steps.
%
\rulename{SClosureCall} assumes that~$\tf$ is mapped
to a closure in~$\sectx$ and evaluates the body of this closure in $n$
steps in the closure environment~$\sectx_\tf$ extended with the value
of its argument~$\tx$ found in~$\sectx$. The resulting value is bound
to~$\ty$ in $\sectx$ to evaluate the remaining term $\sterm$ in~$m$
steps. Hence, the whole term evaluates in~$n + m + 1$~steps.

>>>>

In Figure~\ref{fig:source-definition-base-terms-semantics}, the base
terms are evaluated using a step-indexed big-step semantics whose
judgment~$\seval\sectx\sterm{n}\sclosedvalue$ is read ``Under the
environment~$\sectx$, the base term~$\sterm$ evaluates into the closed
value~$\sclosedvalue$ in~$n$~steps.''
%
\rulename{SVar} looks up in~$\sectx$ to return the closed value of a
variable~$\tx$.
%
\rulename{STuple} looks~$\many\tx$ up in~$\sectx$ to evaluate
tuple~$\stuple{\many\tx}$, binds it to~$\ty$ and continues with
the next term.
%
\rulename{SPrimitiveCall} assumes that~$\tf$ is mapped to a
primitive~$\sprim$ in~$\sectx$ and that $\sprim$ has an associated
interpretation realized as a function~$\tdelta\sprim\param$ from
closed values to closed values. The evaluation of this interpretation
function applied to the value of~$\tx$ is bound to~$\ty$ in~$\sectx$
in order to evaluate the remaining term~$\sterm$ in~$n$ steps. In that
case, the evaluation of the $\textbf{let}$-binding takes~$n + 1$~steps.
%
\rulename{SClosureCall} assumes that~$\tf$ is mapped
to a closure in~$\sectx$ and evaluates the body of this closure in $n$
steps in the closure environment~$\sectx_\tf$ extended with the value
of its argument~$\tx$ found in~$\sectx$. The resulting value is bound
to~$\ty$ in $\sectx$ to evaluate the remaining term $\sterm$ in~$m$
steps. Hence, the whole term evaluates in~$n + m + 1$~steps.
